Final Project Draft (enter actual title later)

### 2022-04-26 initialdraft.Rmd
jocelyn 9:50pm
new draft

---
title: 'finalproj'
author: "Jocelyn, Ana, Cat"
output: 
  html_document:
    keep_md: TRUE
    toc: TRUE
    toc_float: TRUE
    df_print: paged
    code_download: true
---

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = TRUE, error=TRUE, message=FALSE, warning=FALSE)
```

```{r}
library(dplyr)
library(readr)
library(ggplot2)
library(gridExtra)
library(tidyverse)
library(lubridate) 
library(ggthemes)
library(plotly)
library(ggdark)
```

```{r}
healthy_data <- read_csv("healthy_lifestyle_city_2021.csv", 
    col_types = cols(Rank = col_number(), 
        `Sunshine hours(City)` = col_number(), 
        `Cost of a bottle of water(City)` = col_number(), 
        `Obesity levels(Country)` = col_number(), 
        `Life expectancy(years) (Country)` = col_number(), 
        `Pollution(Index score) (City)` = col_number(), 
        `Annual avg. hours worked` = col_number(), 
        `Happiness levels(Country)` = col_number(), 
        `Outdoor activities(City)` = col_number(),
        `Number of take out places(City)` = col_number(), 
        `Cost of a monthly gym membership(City)` = col_number()))

# converting to dollars
healthy_data_dollars <- healthy_data %>% 
  mutate(water_bottle_cost = `Cost of a bottle of water(City)`*1.3,
         gym_cost = `Cost of a monthly gym membership(City)`*1.3)
```

@@

[GDP data source](https://worldpopulationreview.com/countries/countries-by-gdp)

@@

#Starting to mess with hours worked but realized that missing data is going to be a problem
```{r}
ggplot(healthy_data_2, aes(y = fct_reorder(City, `Hours Worked`), x = `Hours Worked`, color = `Happiness levels(Country)`)) +
  geom_point() +
  labs(title = "",
       caption = "Data from: ADD LATER",
       x = "",
       y = "",
       color = "Happiness Level 
       (1-10 scale)") +
  theme(plot.title = element_text(hjust = 1)) +
  theme_classic() 
```

@@

We chose three variables that we think are important contributing factors to overall happiness, influenced of course by where we are and salient factors we feel attuned to. Our variables, life expectancy, sunshine hours, and hours worked, are compared against overall happiness for each place to see if there is a correlation between more or less of each variable. We are also keeping in mind intangible factors such as state of mind and the impacts of cultural attitudes.

@@

```{r, fig.alt= "For this graph, the cities have been placed into bins based on the happiness level and the range they fall into. For example, a country with a happiness level of 4.5 would be placed within the box plot above the "4-5" on the x axis. They are then plotted using upper and lower quartiles to show the distribution of life expectancies."}
bin_size <- 1
healthy_data_dollars %>% 
  select("City" = `City`, "Happiness Level" = `Happiness levels(Country)`, "Life Expectancy" = `Life expectancy(years) (Country)`) %>% 
  arrange(desc(`Life Expectancy`)) %>%

@@

Joce's graph Which cities are the sunniest and least sunny?
```{r, fig.alt = "Graph of the top 10 and bottom 10 cities by annual sunshine hours.The cities are mapped on the y-axis while the sunshine hours is mapped on the x-axis. Cairo, Tel Aviv, and Los Angeles were the top three trending just over 3000 annual sunshine hours while Brussels, Dublin, and Taipei were the bottom three with around 1500 annual sunshine hours."}
top_10 <- healthy_data %>% 
  arrange(desc(`Sunshine hours(City)`)) %>% 
  slice(1:10) %>% 
  ggplot(aes(y = fct_reorder(City,`Sunshine hours(City)`), x = `Sunshine hours(City)`)) +
  geom_col(fill = "khaki") +
  labs(title = "Top 10 and Bottom 10 Cities by Annual Sunshine Hours",
       y = "",
       x = "") +
  dark_theme_minimal()

@@

Ana's graph

@@

```{r, fig.alt= Interactive plot showing the relationship between life expectancy in years and the obesity percentage of each city's respective country}
obesity_life <-
healthy_data_dollars %>% 
  select(`City`, `Life expectancy(years) (Country)`, `Obesity levels(Country)`) %>% 
  arrange(`Obesity levels(Country)`) %>% 
  ggplot(aes(x = `Obesity levels(Country)`, y = `Life expectancy(years) (Country)`, color = `City`))+
  geom_point()+
  labs(title = "Life Expectancy by Country and its Relationship to Obesity Levels ")+
  theme(legend.position = "none",
        panel.background = element_rect(fill = "lightblue",
                                colour = "gray",
                                size = 0.5,
                                ))

@@

>From the graph, we can appreciate a few patterns: There is a slight grouping of cities towards the lower Obesity levels (<10%), that relates to a mid-to-high Life Expectancy. Another cluster is observable in the 20-30% obesity range, with a majority of those cities showing a high life expectancy. It is interesting to note that most of these cities are European, as opposed to other cities at a similar Obesity level, which show lower Life Expectancy and are in the American continent. Finally, we can also observe a last group in the (>30%) Obesity levels, which show a small variation in Life Expectancy, with Washington DC showing the highest Life Expectacy in the group.

>>>>

---
title: 'Final Project Draft (enter actual title later)'
author: "Jocelyn Radke, Ana Espeleta, Cat Terres"
output: 
  html_document:
    keep_md: TRUE
    toc: TRUE
    toc_float: TRUE
    df_print: paged
    code_download: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error=TRUE, message=FALSE, warning=FALSE)
```

```{r}
#Loading the packages
library(dplyr)
library(readr)
library(ggplot2)
library(gridExtra)
library(tidyverse)
library(lubridate) 
library(ggthemes)
library(plotly)
library(ggdark)
```

## Introduction and Background

- Research question: Does money buy happiness?
- Challenging the assumption that the best countries are those that are most economically successful by looking at indicators of well-being instead of just GDP/output/wealth
- Does the amount of sunshine correlate with "happier" people?
- Is there a correlation between life expectancy and happiness?

## Data Collection
- Healthy living report (main source)- [Healthy Lifestyle Cities Report 2021](https://www.kaggle.com/datasets/prasertk/healthy-lifestyle-cities-report-2021)
- GDP info (supplementary source)- [GDP data source](https://worldpopulationreview.com/countries/countries-by-gdp)
- Hours worked info (supplementary source)- [new hours worked data (Penn)](https://worldpopulationreview.com/country-rankings/average-work-week-by-country)

## Analysis

```{r}
#Loading the data
healthy_data <- read_csv("healthy_lifestyle_city_2021.csv", 
    col_types = cols(Rank = col_number(), 
        `Sunshine hours(City)` = col_number(), 
        `Cost of a bottle of water(City)` = col_number(), 
        `Obesity levels(Country)` = col_number(), 
        `Life expectancy(years) (Country)` = col_number(), 
        `Pollution(Index score) (City)` = col_number(), 
        `Annual avg. hours worked` = col_number(), 
        `Happiness levels(Country)` = col_number(), 
        `Outdoor activities(City)` = col_number(),
        `Number of take out places(City)` = col_number(), 
        `Cost of a monthly gym membership(City)` = col_number()))

#Converting to dollars
healthy_data_dollars <- healthy_data %>% 
  mutate(water_bottle_cost = `Cost of a bottle of water(City)`*1.3,
         gym_cost = `Cost of a monthly gym membership(City)`*1.3)
```

@@

@@

#Happiness level by hours worked
```{r}
ggplot(healthy_data_2, aes(y = fct_reorder(City, `Hours Worked`), x = `Hours Worked`, color = `Happiness levels(Country)`)) +
  geom_point() +
  labs(title = "",
       caption = "Data from: ADD LATER",
       x = "",
       y = "",
       color = "Happiness Level 
       (1-10 scale)") +
  theme(plot.title = element_text(hjust = 1)) +
  theme_classic() 
```

@@

> We chose three variables that we think are important contributing factors to overall happiness, influenced of course by where we are and salient factors we feel attuned to. Our variables, life expectancy, sunshine hours, and hours worked, are compared against overall happiness for each place to see if there is a correlation between more or less of each variable. We are also keeping in mind intangible factors such as state of mind and the impacts of cultural attitudes.

@@

```{r, fig.alt= "For this graph, the cities have been placed into bins based on the happiness level and the range they fall into. For example, a country with a happiness level of 4.5 would be placed within the box plot above the 4-5 on the x axis. They are then plotted using upper and lower quartiles to show the distribution of life expectancies."}
bin_size <- 1
healthy_data_dollars %>% 
  select("City" = `City`, "Happiness Level" = `Happiness levels(Country)`, "Life Expectancy" = `Life expectancy(years) (Country)`) %>% 
  arrange(desc(`Life Expectancy`)) %>%

@@

Joce's graph- Which cities are the sunniest and least sunny?
```{r, fig.alt = "Graph of the top 10 and bottom 10 cities by annual sunshine hours.The cities are mapped on the y-axis while the sunshine hours is mapped on the x-axis. Cairo, Tel Aviv, and Los Angeles were the top three trending just over 3000 annual sunshine hours while Brussels, Dublin, and Taipei were the bottom three with around 1500 annual sunshine hours."}
top_10 <- healthy_data %>% 
  arrange(desc(`Sunshine hours(City)`)) %>% 
  slice(1:10) %>% 
  ggplot(aes(y = fct_reorder(City,`Sunshine hours(City)`), x = `Sunshine hours(City)`)) +
  geom_col(fill = "khaki") +
  labs(title = "Top 10 and Bottom 10 Cities by Annual Sunshine Hours",
       y = "",
       x = "") +
  dark_theme_minimal()

@@

Ana's graph
- maybe make this one a plotly?

@@

```{r, fig.alt= "Interactive plot showing the relationship between life expectancy in years and the obesity percentage of each city's respective country"}
obesity_life <-
healthy_data_dollars %>% 
  select(`City`, `Life expectancy(years) (Country)`, `Obesity levels(Country)`) %>% 
  arrange(`Obesity levels(Country)`) %>% 
  ggplot(aes(x = `Obesity levels(Country)`, y = `Life expectancy(years) (Country)`, color = `City`))+
  geom_point()+
  labs(title = "Life Expectancy by Country and its Relationship to Obesity Levels ")+
  theme(legend.position = "none",
        panel.background = element_rect(fill = "lightblue",
                                colour = "gray",
                                size = 0.5,
                                ))

@@

> From the graph, we can appreciate a few patterns: There is a slight grouping of cities towards the lower Obesity levels (<10%), that relates to a mid-to-high Life Expectancy. Another cluster is observable in the 20-30% obesity range, with a majority of those cities showing a high life expectancy. It is interesting to note that most of these cities are European, as opposed to other cities at a similar Obesity level, which show lower Life Expectancy and are in the American continent. Finally, we can also observe a last group in the (>30%) Obesity levels, which show a small variation in Life Expectancy, with Washington DC showing the highest Life Expectacy in the group.
